Comparison of three similarity scores for bullet LEA matching\tnoteref{t1}\tnoteref{t2}

### 2019-12-09 index.Rnw
Binary decision model

This threshold system introduces a binary classification: identification or exclusion. This definition of error is more stringent than the AFTE Theory of Identification, in that it does not allow for inconclusive results. This increased rigor may increase the error rate of the model when compared to examiner error rates, but we expect that the increased information available from the 3D measurement data will compensate for this loss. A binary decision model is also easier to interpret and provides more clear-cut, definitive results than the AFTE Theory of Identification system used in most forensic laboratories in the United States. Of course, in jurisdictions which utilize score-based likelihood ratios, this threshold system is not necessary because likelihood ratios are evaluated on a continuous spectrum (though, there is a natural threshold at 1, and many times a more flexible threshold is used to determine the level of significance of a result). Working under the binary decision model common in US jurisdictions, we can enumerate characteristics of an ideal similarity scoring mechanism:

>>>>

This threshold system introduces a binary classification: identification or exclusion. This definition of error is more stringent than the AFTE Theory of Identification, in that it does not allow for inconclusive results. This increased rigor may increase the error rate of the model when compared to examiner error rates, but we expect that the increased information available from the 3D measurement data will compensate for this loss. A binary decision model is also easier to interpret and provides more clear-cut, definitive results than the AFTE Theory of Identification system used in most forensic laboratories in the United States. Of course, in jurisdictions which utilize score-based likelihood ratios, this threshold system is not necessary because likelihood ratios are continuous. Even with likelihood ratios, however, there is a natural threshold at 1, and many times a more flexible threshold (100, 1000) is used to determine the weight given to a result.

The remainder of this paper will utilize the binary decision model common in US jurisdictions. With this model, we can enumerate characteristics of an ideal similarity scoring mechanism:
